Karpov, Kasprov, Anand

### 2022-05-10 inst/kka.Rmd
typo

```{r anamwa}
M <- rbind(a1,rev(a2))
dimnames(M) <- list(karpov_plays=c("White","Black"),result=c("karpov wins","karpov draws","kaprov loses"))
M
fisher.test(M)
```

>>>>

```{r anamwa}
M <- rbind(a1,rev(a2))
dimnames(M) <- list(karpov_plays=c("White","Black"),result=c("karpov wins","karpov draws","karpov loses"))
M
fisher.test(M)
```
